\section{Consistency study}
In this section, we investigate the effect of changing
$\delta_{\rm sl}$ in the continuous, neutral model.
In all this section we will assume that
$z_0$ is constant.
The main direct changes when $\delta_{\rm sl}$ becomes
$\delta_{\rm sl}' < \delta_{\rm sl}$ are:
\begin{itemize}
\item the Coriolis effect and the large-scale forcing are
now taken into account for $z \in 
[\delta_{\rm sl}', \delta_{\rm sl}]$;
\item the viscosity $K(z)$ for $z \in 
[\delta_{\rm sl}', \delta_{\rm sl}]$ is not forced by the law
of the wall anymore.
\end{itemize}
There are also indirect effects due to the non-linearity of the
problem:
\begin{itemize}
	\item Even if the bulk algorithm is well designed and returns
		the same friction scales whether it takes as input
		$(\delta_1, u_2(\delta_1))$ or 
		$(\delta_2, u_2(\delta_2))$ (which is assumed to
		be the case),
		the input differs between $u_1$ and $u_2$ because
		of the direct effects.
\end{itemize}

\subsection{Study of the consistency: neutral case}
Let $\delta_1$,$\delta_2$ two
different heights of surface layer
such that $\delta_1 < \delta_2$.

Let $u_1$, $u_2$, be solutions of 
\eqref{eq:ND_NeutralCase_continuousModel} using
respectively $\delta_1, \delta_2$ for $\delta_{sl}$.

\subsubsection{Analytical study assuming identical viscosities}
First, note that inside the surface layer for $u_2$,
since $u_2(z) = \frac{u_\star}{\kappa}\log(1+\frac{z}{z_0})
\frac{u_2(\delta_{2})}{||u_2(\delta_{2})||}$, assuming
$||u_2(\delta_{2})||$ follows the same log low (it only works
when the problem is continuous in time)
\begin{equation}
(\partial_t + if) u_2(z) = \frac{\log(1+\frac{z}{z_0})}
{\log(1+\frac{\delta_2}{z_0})}(\partial_t + if) u_2(\delta_2), 
~~~\forall z \leq \delta_2
\end{equation}
Let us assume that $K\partial_z u_2$ is $C^1$ at $\delta_2$;
then $\partial_z (K\partial_z u_2) = 0$ in all the interval
$(0, \delta_2)$ and the evolution equation of $u_2$ in
$(\delta_1, \delta_2)$ is
\begin{equation}
(\partial_t + if) u_2(z) = \frac{\log(1+\frac{z}{z_0})}
{\log(1+\frac{\delta_2}{z_0})} i f u_G, 
	~~~\forall z \in (\delta_1, \delta_2).
\end{equation}
The difference between $u_1$ and $u_2$ is governed by this interval:
substracting the two evolution equations gives
\begin{equation}
(\partial_t + if) (u_2 - u_1) = \left(\frac{\log(1+\frac{z}{z_0})}
{\log(1+\frac{\delta_2}{z_0})} - 1\right)i f u_G 
-
\partial_z (K \partial_z u_1), ~~~\forall z \in (\delta_1, \delta_2).
\end{equation}
We see in the right hand side of the latter equation the two items
of the begining of the section:
the large-scale forcing with the Coriolis effect,
and the diffusion term of $u_1$ which is actually
$\partial_z (K \partial_z u_1) = \partial_z (K \partial_z u_1 - K \partial_z u_2)$

Let $w=u_2 - u_1$. If we assume that $K$ is the viscosity for both
$u_2$ and $u_1$ then
\begin{equation}
	\begin{cases}
		(\partial_t + if) w = \partial_z (K \partial_z w) ,
		~~ \forall z > \delta_2 \\
(\partial_t + if) w = \partial_z (K \partial_z w) + \left(\frac{\log(1+\frac{z}{z_0})}
{\log(1+\frac{\delta_2}{z_0})} - 1\right)i f u_G 
, ~~~\forall z \in (\delta_1, \delta_2) \\
		K \partial_z w = \frac{\kappa}
		{\log(1+\frac{\delta_1}{z_0})}\left(
		u_{\star, 2} u_2(\delta_1) -
		u_{\star, 1} u_1(\delta_1)\right),
		~~~ \forall z \leq \delta_1.
	\end{cases}
\end{equation}
Apart from the bulk sensitivity in the surface condition,
the difference is hence from the forcing
$\left(\frac{\log(1+\frac{z}{z_0})}
{\log(1+\frac{\delta_2}{z_0})} - 1\right)i f u_G$.
This forcing is more important when $\frac{\delta}{z_0}$
is small.
\subsubsection{Semi-Discrete Consistency (Finite Differences)}
This subsection shows that the semi-discrete in space
Finite Differences
scheme is not sensitive to the value of $\delta_{\rm sl}$.
We put aside the sensitivity of the bulk procedure by
assuming that $z_{0M}$ is a constant.
%
The approach used in Finite Differences consists in assuming
$\delta_{\rm sl} = z_{1/2}$ and to use the flux at $z_0$ in
the integration in time
$K_0\phi_0 = u_\star^2
\frac{u(\delta_{\rm sl})}{||u(\delta_{\rm sl})||}$
(we assume that $u(0)=0$ for simplicity).
We generalize the usual approach with
$\delta_{sl} = z_{1/2} - \epsilon$ with
$\epsilon < \frac{h_{\frac{1}{2}}}{2}$. 
The value $u(\delta_{\rm sl})$ can be approximated
by $u_{1/2} - (\partial_z u)(\delta_{\rm sl})\epsilon$.
The implementation of such a boundary condition would be
\begin{equation}
	\label{eq:ND_Consistency_SemiDiscreteBdCond}
K_0\phi_0 = 
\kappa^2 ||u_{1/2} - (\partial_z u)(\delta_{\rm sl})\epsilon ||
	\frac{u_{1/2} - (\partial_z u)(\delta_{\rm sl})\epsilon 
}{\log(1+\frac{\delta_{sl}}{z_{0M}})^2}
\end{equation}
and it becomes convenient to compute the difference between
$\delta_{sl}=z_{1/2}$ and $\delta_{sl}'=z_{1/2}-\epsilon$.
Indeed,
$|u - (\partial_z u) \epsilon| = |u| -
\epsilon \frac{\mathfrak{R}(\overline{u} \partial_z u)}{|u|}
+ O(\epsilon^2)$ so
$|u - (\partial_z u) \epsilon|(u - (\partial_z u) \epsilon) =
|u|u -
\epsilon \left(
u\frac{\mathfrak{R}(\overline{u} \partial_z u)}{|u|}
+ |u| \partial_z u
\right)
+ O(\epsilon^2)$.
Using the wall law
$\partial_z u=\frac{u(\delta_{\rm sl})}{(\delta_{\rm sl} + z_0)
\log(1+\frac{\delta_{sl}}{z_0})}$ we obtain 
\begin{equation}
|u - (\partial_z u) \epsilon|(u - (\partial_z u) \epsilon) - |u|u =
	- \epsilon \left(\frac{2|u_{1/2}|u_{1/2}}
	{(\delta_{\rm sl} + z_0) \log(1+\frac{\delta_{sl}}{z_0})}
	\right)+ O(\epsilon^2)
\end{equation}
Combining with $\frac{\kappa^2}{\log(1+\frac{\delta_{sl}}{z_0})}$,
we find the derivative of the right-hand side of
\eqref{eq:ND_Consistency_SemiDiscreteBdCond} with respect to
$\delta_{sl}$ to be equal to zero.
In conclusion, if $z_{0M}$ does not depend on $u$ and if
the evolution equation is integrated in time at $z_\frac{1}{2}$,
then for the Finite Differences scheme
\begin{equation}
	\partial_{\delta_{sl}} (K_0 \phi_0) = 0.
\end{equation}
This result is expected since in the boundary condition
$K_0 \phi_0 = u_\star^2 e_\tau$ the orientation $e_\tau$ is
not changed by the use of the wall law for $\partial_z u$
and the friction scale $u_\star$ is not affected because
$u(z_\frac{1}{2} - \epsilon)$ is given by the wall law.
\subsection{Study of the consistency: stable case}
\subsection{Study of the consistency: unstable case}
